Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/compilation.tex
adding information about us only compiling to ABGP to implementation

We handle these challenges by breaking compilation into multiple stages and developing efficient algorithms for each (See Figure~\ref{fig:pipeline}). The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR). Policies in RIR are checked for well-formedness (\EG, never constraining traffic that does not enter the network), before being combined with the network topology to obtain the Product Graph Intermediate Representation (PGIR). The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions. We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes. Once the compiler determines that the PGIR is safe, it translates it to an abstract BGP (ABGP) representation. Our current \sysname compiler produces ABGP configurations, however vendor-specific adaptors to translate from ABGP to concrete device configurations could easily be added.

>>>>

We handle these challenges by breaking compilation into multiple stages and developing efficient algorithms for each (See Figure~\ref{fig:pipeline}). The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR). Policies in RIR are checked for well-formedness (\EG, never constraining traffic that does not enter the network), before being combined with the network topology to obtain the Product Graph Intermediate Representation (PGIR). The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions. We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes. Once the compiler determines that the PGIR is safe, it translates it to an abstract BGP (ABGP) representation. Vendor-specific adaptors to translate from ABGP to concrete device configurations are easily added to generate concrete configurations.

### 2016-01-29 paper/implementation.tex
adding information about us only compiling to ABGP to implementation

We have written a prototype compiler for \sysname that is implemented in roughly 5500 lines of F\# code. Users of \sysname only ever see the high-level constraint-based language presented in Section~\ref{sec:motivation}. The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the commonly used no-export community, as well as for ensuring at least k-failure safety for user-specified aggregates. Finally, since each prefix has a separate routing policy, the \sysname compiler is able to compile each routing policy in parallel.

>>>>

We have written a prototype compiler for \sysname that is implemented in roughly 5500 lines of F\# code. The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the no-export community, as well as for ensuring at least k-failure safety for user-specified aggregates. Since each prefix has a separate routing policy, the \sysname compiler is able to compile each routing policy in parallel. The current compiler produces only ABGP policies, which can be incorporated into an existing template-based system, for example by mixing the \sysname configuration with other configuration components, or by generating vendor-specific configurations.
